The Galactic Midplane Is Not a Plane: Implications for Dynamical Analysis with {\em Gaia} Data and Beyond

### 2019-04-26 paper/ms.tex
Shuffle author order
Update caption to chervin midplane plot

\begin{figure*}
\begin{center}
\includegraphics[width=342.078286667pt]{fig/midplane_fit_chervinsim.pdf}
\end{center}
\caption{The local midplane determined at the fiducial Solar radius
($8.2\,\kpc$) for 4 different time steps from previously run toy simulations
of a Sagittarius encounter with the Milky Way \citep{2018MNRAS.481..286L}. As
before, we have subtracted the best fit $A\sin{(\phi+B)}+C$ curve to account
for inaccuracies in the galactocentric coordinate system. Error bars are
calculated as in Figure~\ref{fig:midplane}. (\Gus{Guessing here, need to
figure out what the panels actually show:}) The left two panels show the
midplane as a function of azimuth before the first encounter. As later
encounters occur, we can see that stronger midplane variations result. In
fact, one can see that an $m=2$ mode is excited in the third panel --- this is
consistent with Figure~17 of \citet{2018MNRAS.481..286L}, which shows that an
$m=2$ mode is excited (note that $m=0$ and $m=1$ modes are stronger, but these
are removed in our sine-curve subtraction).}
\label{fig:midplane_chervin}
\end{figure*}

>>>>

\begin{figure*}
\begin{center}
\includegraphics[width=342.078286667pt]{fig/midplane_fit_chervinsim.pdf}
\end{center}
\caption{The local midplane determined at the fiducial Solar radius
($8.2\,\kpc$) for 4 different time steps from previously run toy simulations
of a Sagittarius encounter with the Milky Way \citep{2018MNRAS.481..286L}. As
before, we have subtracted the best fit $A\sin{(\phi+B)}+C$ curve to account
for inaccuracies in the galactocentric coordinate system. Error bars are
calculated as in Figure~\ref{fig:midplane}. (\Gus{Check:}) The {\em upper}
panels show the midplane as a function of azimuth before the first encounter
near the Solar circle. As later encounters occur which bring the
Sagittarius-like object closer to the Solar circle, we can see that stronger
midplane variations result. In fact, one can see that an $m=2$ mode is excited
in the third panel --- this is consistent with Figure~17 of
\citet{2018MNRAS.481..286L}, which shows that an $m=2$ mode is excited (note
that $m=0$ and $m=1$ modes are stronger, but these are removed in our
sine-curve subtraction). The fact that the $t=6.9\,\Gyr$ panel looks
qualitatively similar to the panels from the FIRE simulations
(Figure~\ref{fig:midplane}) is evidence that the midplane variations are
produced in part by mergers.}
\label{fig:midplane_chervin}
\end{figure*}
